The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/ms.tex
L426

Figure \ref{fig:ebin-idist} shows that when low mutual inclinations are preferred as an initial condition, the fraction of systems that result in a polar orbit drop dramatically, and that this effect is fairly consistent across values for $e_\text{b}$. Figure \ref{fig:fpol_j-idist} similarly shows this effect, but with an interesting caveat: in the model with the heaviest preference for coplanar initial conditions, the fraction of polar disks is fairly high when $j=0$ and $e_\text{b}$ has either a uniform of thermal distribution ($>0.5$ in the thermal case).

>>>>

Figure \ref{fig:ebin-idist} shows that when low mutual inclinations are preferred as an initial condition, the fraction of systems that result in a polar orbit drop\RR{s} dramatically, and that this effect is fairly consistent across values for $e_\text{b}$. Figure \ref{fig:fpol_j-idist} similarly shows this effect, but with an interesting caveat: in the model with the heaviest preference for coplanar initial conditions, the fraction of polar disks is fairly high when $j=0$ and $e_\text{b}$ has either a uniform of thermal distribution ($>0.5$ in the thermal case).

### 2025-04-04 src/tex/review.tex
L445
L426

>>>>

    \begin{response}
        {L426: drops instead of drop?}
        This has been fixed. Thank you for catching it.
    \end{response}

    \begin{response}
        {L445: In the definition of f, is M meant to be M\_b or M\_1 + M\_2? It is likely the latter one. Unless I am mistaken, it was not defined earlier.}
        It is supposed to be $M_\text{b}\equiv M_1 + M_2$. We have added text for clarification.
    \end{response}
